Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-19 FIE2019-final-TPJHD.tex
Shortened school section and abstract

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. This paper address the key questions ``What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?'' and ''Can accreditation by Professional, Statutory and Regulatory Bodies(PSRBs) enhance the provision of cybersecurity within a bodies jurisdiction?''.

@@

The paper proposes a number of recommendations for future cybersecurity educational initiatives, interventions and research, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}; this is alongside a wider focus on computer science education reform, especially across the UK~\cite{crick+sentance:2011,brown-et-al:sigcse2013,brown-et-al:toce2014,wgictreview:2013,moller+crick:jce2018,davenport-et-al:latice2016,murphy-et-al:programming2017,simon-et-al:sigcse2018,tryfonas+crick:petra2018}. There has been a recent Association for Computing Machinery (ACM)  working group as part of the Conference on Innovation and Technology in Computer Science Education \cite{Parrishetal2018a}, but this has yet to report.  The intention of this working group is to develop a taxonomy for approaches to cybersecurity education. The third aim of this working group is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.

@@

\IEEEtriggeratref{51}

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations 
%- from national academies, learned societies and even governments -- 
have been presented and discussed in recent years, with varying levels of impact on policy and practice. This paper address the key questions ``What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science students?'' , ``Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?'' and ''Can accreditation by Professional, Statutory and Regulatory Bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?''.

@@

%The paper proposes a number of recommendations for future cybersecurity educational initiatives, interventions and research, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}; this is alongside a wider focus on computer science education reform, especially across the UK~\cite{%crick+sentance:2011,brown-et-al:sigcse2013,
brown-et-al:toce2014,%wgictreview:2013,moller+crick:jce2018,davenport-et-al:latice2016,
murphy-et-al:programming2017%,simon-et-al:sigcse2018,tryfonas+crick:petra2018
}. There has been a recent Association for Computing Machinery (ACM)  working group as part of the Conference on Innovation and Technology in Computer Science Education \cite{Parrishetal2018a}, but this has yet to report.  The intention of this working group is to develop a taxonomy for approaches to cybersecurity education. The third aim of this working group is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.

@@

\IEEEtriggeratref{44}
